---
title: "Depth from Pressure"
author: "David Kaiser"
date: "2018/01/18"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("depth_from_pressure_DK.R")
```

## Description

A function to calculate **depth from pressure** according to UNESCO Technical Papers in Marine Science No. 44. This is the way that Seabird Electronics (SBE) CTD systems calculate depth (<http://www.seabird.com/document/an69-conversion-pressure-depth>).
**Latitude** can optionally be supplied to correct for gravity variation with latitude. If latitude is not supplied standard gravity will be used.

## Arguments

*pressure* -- *in situ* pressure in dbar

*latitude* -- optional; used to calculate gravity variation with latitude

## Value

*depth in m*

## Example

without latitude supplied
```{r example, echo=TRUE}
depth.from.pressure.DK(pressure = 10)
```

with latitude supplied
```{r example_extended, echo=TRUE}
depth.from.pressure.DK(pressure = 10, latitude = 10)
```